A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex

\begin{itemize}
\item Escape Hatch: \c{eval(unlock_binding ... )} to prevent R CMD check warnings
\item Accessing data frame columns like local variables: \c{eval(x + y + z, data.frame(x, y z))}
\item Poor man's sandboxing: local function
\item Assembling call strings from components passed by callers: eval(substitute(f(x, y, z)))
\item Convenience: 
\item Dynamic code loading: \c{eval(parse(...))}. The textual input in parse can come from three places: a string, a file or in interactive R sessions directly from user input. Next to \c{parse}, there are also \c{str2expression} and \c{str2lang} which are a specialized versions of parse that do not keep source references and thus are a bit faster.
\item bypassing R CMD check in the case one accesses dangerous functions such as unlockBinding or private symbols.
\item evaling recorded calls in model-fitting functions or passing most of the current call to another function. Both ``patterns'' use the \c{match.call} to capture current call. The latter is just for laziness as it is the same as calling the new function with explicitly selecting the arguments.
\end{itemize}

>>>>

\begin{itemize}
\item Escape Hatch: \c{eval(unlock_binding ... )} to prevent R CMD check warnings
  \subsubsection{Evaluation using Data Fields}
  A common use of \eval is to evaluate expressions that access data frame
columns or list (heterogeneous vectors) elements by name. Core R provides two
functions, \c{with} and \c{within} that implement this pattern. These functions
construct a temporary environment with data frame columns or list elements as
the bindings. Side-effects performed by the evaluated expression take place in
this temporary environment and are ignored by the \c{with} function. The
\c{within} function copies these modifications to a local copy of the input data
and returns it. This pattern is used quite often for statistical modeling. The
modeling expressions is constructed from variable names whose values are
supplied by a data frame or list.

\item Poor man's sandboxing: local function
\item Assembling call strings from components passed by callers: eval(substitute(f(x, y, z)))
\item Convenience: 
\item Dynamic code loading: \c{eval(parse(...))}. The textual input in parse can come from three places: a string, a file or in interactive R sessions directly from user input. Next to \c{parse}, there are also \c{str2expression} and \c{str2lang} which are a specialized versions of parse that do not keep source references and thus are a bit faster.
\item bypassing R CMD check in the case one accesses dangerous functions such as unlockBinding or private symbols.
\item evaling recorded calls in model-fitting functions or passing most of the current call to another function. Both ``patterns'' use the \c{match.call} to capture current call. The latter is just for laziness as it is the same as calling the new function with explicitly selecting the arguments.
\end{itemize}
